Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-09-17 main.tex
Add acknowledgement to the helpers in the experiments.
Corrected the bicycle name, fixes #7.

\section{Methods}
%
\subsection{Bicycle}
%
We modified an electric bicycle (Grenoble Arroyo, Royal Dutch Gazelle, Dieren,
The Netherlands) with a custom motor in the steering assembly capable of
applying up to 7~\si{\newton\meter} of torque between the head tube and steer
tube, see Figure~\ref{fig:balance-assist-bicycle}. A custom motor controller
converts the commanded torque to applied torque. We measure the speed of the
rear wheel with an encoder (Magura XXX) and measure the body fixed roll rate of
the bicycle with a MEMs rate gyroscope (BN0086, Sparkfun, Niwot, USA). The
balance assist control algorithm is implemented on a microprocessor (Teensy,
PJRC, USA) and data from all sensors is logged with a CAN bus (CanEdge2, CSS
Electronics, Denmark) at at least 100 Hz.

@@

\section*{Acknowledgements}
%
This study follows and draws from experimental and analysis methods originally
developed in unpublished research by Marco Reijne. The authors acknowledge
Felix Dauer, David Gabriel, Sierd Heida, Oliver Maier, Maarten Pelgrim, Marco
Reijne, and Arend Schwab for contributions to the development of the balance
assist bicycle.

>>>>

\section{Methods}
%
\subsection{Bicycle}
%
We modified an electric bicycle (Grenoble C8 HMB, Royal Dutch Gazelle, Dieren,
The Netherlands) with a custom motor in the steering assembly capable of
applying up to 7~\si{\newton\meter} of torque between the head tube and steer
tube, see Figure~\ref{fig:balance-assist-bicycle}. A custom motor controller
converts the commanded torque to applied torque. We measure the speed of the
rear wheel with an encoder (Magura XXX) and measure the body fixed roll rate of
the bicycle with a MEMs rate gyroscope (BN0086, Sparkfun, Niwot, USA). The
balance assist control algorithm is implemented on a microprocessor (Teensy,
PJRC, USA) and data from all sensors is logged with a CAN bus (CanEdge2, CSS
Electronics, Denmark) at at least 100 Hz.

@@

\section*{Acknowledgements}
%
This study follows and draws from experimental and analysis methods originally
developed in unpublished research by Marco Reijne. The authors acknowledge
Felix Dauer, David Gabriel, Sierd Heida, Oliver Maier, Maarten Pelgrim, Marco
Reijne, and Arend Schwab for contributions to the development of the balance
assist bicycle. We thank all of the assistants that helped run the experiments
and the subjects for their time an enthusiasm.
